### 2022-01-21 input/proposal.tex
meow

\begin{definition}[\label{def:fs}\underline{F}orwarding of
  \underline{s}taleness (FS)]
  %
  Any source can broadcast a staleness notification at any
  time. Every \process $x$ delivers and forwards a received staleness
  notification if it targets its best up-to-date delivered message:
  %% \TODO{$(\delta_s \in R_x \wedge \alpha_s =
  %%     \textup{minUTD}~D_x) \iff \eventually (d_x(\delta_s) \rightarrow
  %% f_x(\delta_s))$.}
  $(\last D_x = \alpha_s \wedge d_x(\alpha_s) \rightarrow
  r_x(\delta_s)) \implies d_x(\delta_s) \rightarrow f_x(\delta_s)$.
  % \wedge \nexists d'_s: d_x(\delta_s) \TODO{\not\rightarrow} d_x(\delta_s'))$.
\end{definition}

\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos] FB where
  a \process $x$ that receives but does not deliver a staleness
  notification sends back --~or echoes~-- its best up-to-date
  delivered message: $(\last D_x = \alpha_s^d \wedge \delta_s
  \not\in D_x \wedge d_x(\alpha_s^d)\rightarrow r_{xy}(\delta_{s'}))
  \implies r_{xy}(\delta_{s'}) \rightarrow
  s_{xy}(\alpha_s^d\oplus^{w_{xy}})$.

@@

A first step to avoid staying in inconsistent state is to extend the
behavior of each \process so \processes such as $c$, that would remain
in a wrong partition, use their history of receipt and delivery to
detect the blocking of staleness notifications that can hinder
reaching consistent partitioning.  In Figure~\ref{fig:problem}, $b$
blocked the staleness notification $\delta_a$ that $c$ needs since it
belongs to a ephemeral partition $P_c$ that $c$ acknowledges to be
stale before $b$ does. Therefore, $c$ can detect the blocking of
$\delta_a$ since it acknowledges that its parent $b$ received,
delivered, and forwarded the stale notification $\alpha_c^1$. In other
terms, $c$ acknowledges that between the delivery of $\alpha_c^1$ and
the delivery of $\delta_c$, $b$ blocked any other $\delta$ and
therefore, it could have blocked $\delta_a$.

@@

\begin{lemma}[\label{lem:detector}$\textup{FB}^+ \wedge \textup{FS}
  \implies$ Detector existence] Assuming
  $\textup{FB}^+$ and $\textup{FS}$, a chain of delivery on $\pi_{xz}$ of
  $\alpha_x$ with $\alpha_x = \last D_z$, if $x$ broadcasts a staleness
  notification $\delta_x$, either
  \begin{inparaenum}[(A)]
  \item\label{lem:detectorA}  $z$ eventually delivers it, or 
  \item\label{lem:detectorB} a \process $y$ in such a chain of
    delivery $\pi_{xz}'$ eventually acknowledges its blocking.
  \end{inparaenum}
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}

>>>>

\begin{definition}[\label{def:fs}\underline{F}orwarding of
  \underline{s}taleness (FS)]
  %
  Any source can broadcast a staleness notification at any time. Every
  \process $x$ delivers and forwards a received staleness notification
  $\delta_s$ if it targets its best up-to-date delivered message:
  %% \TODO{$(\delta_s \in R_x \wedge \alpha_s =
  %%     \textup{minUTD}~D_x) \iff \eventually (d_x(\delta_s) \rightarrow
  %% f_x(\delta_s))$.}
  $(\last D_x = \alpha_s \wedge d_x(\alpha_s) \rightarrow
  r_x(\delta_s)) \implies d_x(\delta_s) \rightarrow f_x(\delta_s)$.
  % \wedge \nexists d'_s: d_x(\delta_s) \TODO{\not\rightarrow} d_x(\delta_s'))$.
\end{definition}

\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos]
  In addition to FB, a \process $x$ that receives but does not deliver
  a staleness notification $\delta_{s}$ sends back --~or echoes~-- its
  best up-to-date delivered message: $(\last D_x = \alpha_{s'}^d
  \wedge \delta_{s'} \not\in D_x \wedge d_x(\alpha_{s'}^d)\rightarrow
  r_{xy}(\delta_{s})) \implies r_{xy}(\delta_{s}) \rightarrow
  s_{xy}(\alpha_{s'}^d\oplus^{w_{xy}})$.

@@

A first step to avoid staying in inconsistent state is to extend the
behavior of each \process so \processes such as $c$, that would remain
in a wrong partition, use their history of receipt and delivery to
detect the possible blocking of staleness notifications that can
hinder reaching consistent partitioning.  In Figure~\ref{fig:problem},
$b$ blocked the staleness notification $\delta_a$ that $c$ needs since
it belongs to a ephemeral partition $P_c$ that $c$ acknowledges to be
stale before $b$ does. Therefore, $c$ can detect the possible blocking
of $\delta_a$ since it acknowledges that its parent $b$ received,
delivered, and forwarded the stale notification $\alpha_c^1$. In other
terms, $c$ acknowledges that between the delivery of $\alpha_c^1$ and
the delivery of $\delta_c$, $b$ blocked any other $\delta$ and
therefore, it could have blocked $\delta_a$.

@@

\begin{lemma}[\label{lem:detector}$\textup{FB}^+ \wedge \textup{FS}
  \implies$ Detector existence] Assuming
  $\textup{FB}^+$ and $\textup{FS}$, a chain of delivery on $\pi_{xz}$ of
  $\alpha_x$ with $\alpha_x = \last D_z$, if $x$ broadcasts a staleness
  notification $\delta_x$, either
  \begin{inparaenum}[(A)]
  \item\label{lem:detectorA}  $z$ eventually delivers it, or 
  \item\label{lem:detectorB} a \process $y$ in such a chain of
    delivery $\pi_{xz}'$ eventually detects the possible blocking of $\delta_x$.
  \end{inparaenum}
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}
